---
title: "Validation"
author: "Tommaso Becchi"
date: "19/2/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("GEOquery")
library(dplyr)
library("pheatmap")
library("ggplot2")
library("limma")
library("edgeR")
library("psych")
library("igraph")
library("knitr")
library("pROC")
```



### 6. GENE NETWORK VALIDATION

```{r}
string<-read.table("string_homosapiens.txt",sep=" ",header=T)
string<-string[string$coexpression>0,c(1,2,6)]
head(string)
dim(string)

```

```{r}
comparison
```
This table shows the best thresholds selected in the previous paragraphs. Using these thresholds I create the new dataframes to use for the validation.

```{r}
pearson_l<-final_data_p[abs(final_data_p$cor)>=0.6,]
pearson_nl<-final_data_NL_p[abs(final_data_NL_p$cor)>=0.75,]
kendall_l<-final_data_k[abs(final_data_k$cor)>=0.53,]
kendall_nl<-final_data_NL_k[abs(final_data_NL_k$cor)>=0.55,]
spearman_l<-final_data_s[abs(final_data_s$cor)>=0.64,]
spearman_nl<-final_data_NL_s[abs(final_data_NL_s$cor)>=0.55,]

head(pearson_l)
```

#### 6.1 IDs conversion

STRING dataframe uses ENSP identifier but my dataframes have the ENSG ones. This is a problem because the names need to be of the same type to verify which interactions are present in both networks.

```{r}
#Create a vector with all the ENGS identifiers in my database
gen_id<-c(pearson_l[,1],pearson_l[,2])
#Remove all the duplicates
gen_un<-unique(gen_id)
length(gen_un)
```
In my dataframe there are 588 different ENSG genes

```{r}
#Convert ENGS in ENSP using Biomart
biomart <- getBM(attributes=c('ensembl_gene_id',"ensembl_peptide_id"), filters = 'ensembl_gene_id', values =gen_un, mart = hsmart)
dim(biomart)

```
Biomart contains more than 586 identifiers because to each ENSG correspond more than one ENSP. This is a problem because I want a unique ENSG-ENSP conversion.
Next steps aim to detect which ENSP identifiers I have to use.

```{r}
#Remove "9606." from each STRING identifier
string$p1<-substr(string$protein1,6,20)
string$p2<-substr(string$protein2,6,20)

#Detect which of my 2912 ENSP identifiers are present in STRING
try<-biomart$ensembl_peptide_id %in% (string$p2)
summary(try)
```
The 513 ENSP identifiers that are present both in my BIOMART table and in STRING are the ones that are useful for further analyses.

```{r}
#Create a "conversion table" usign only the ENSP identifier that are present in both BIOMART and  STRING dataframes"
both<-biomart[try==T,]
head(both)
```
```{r}
# These 2 "for cycles" aim to add the colums with ENSP identifiers to pearson_l. If ENSG identifiers are present in BOTH they have a correspondent ENSP in STRING and I use BOTH to convert them. If they are not present in BOTH, they do not have a correspondent ENSP in STRING and i add a " " in ENSP column

l<-c()
for (k in pearson_l$row){
  if (k %in% both$ensembl_gene_id){
    pep<-both[both$ensembl_gene_id==k,2]
    l<-c(l,pep)
  }
  else{
    l<-c(l,"")
  }
}
pearson_l$p1<-l

l<-c()
for (k in pearson_l$column){
  if (k %in% both$ensembl_gene_id){
    pep<-both[both$ensembl_gene_id==k,2]
    l<-c(l,pep)
  }
  else{
    l<-c(l,"")
  }
}
pearson_l$p2<-l

head(pearson_l)

```
#### 6.2 ROC graph
```{r}
pearson_l$check <- ifelse(is.na(match(paste0(pearson_l$p1, pearson_l$p2),paste0(string$p1, string$p2))), FALSE, TRUE)
summary(pearson_l$check)


plot.roc(pearson_l$check,pearson_l$cor,percent=T)
