---
title: "From normalized to final"
author: "Tommaso Becchi"
date: "14/5/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

### LIBRARIES
```{r}
library("GEOquery")
library(dplyr)
library("limma")
library("edgeR")
library("psych")
library("knitr")
library("pROC")
library("minet")
library("entropy")
library("WGCNA")
library("infotheo")
library("igraph")
library("tidyr")
library("STRINGdb")
library("visNetwork")
```


### 0. INPUT DATA (CQN NORMALIZED DEGs COUNT)
```{r}
normalized_count_AL<-read.csv("normalized_count_AL",row.names = 1)
normalized_count_NL<-read.csv("normalized_count_NL",row.names = 1)
```

### 1.1 SCORES
```{r}
flattenCorrMatrix <- function(cormat) {
  ut <- upper.tri(cormat)
  return(data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut]
  ))
}
```

```{r}
scores<-function(tab){
  #### Kendall
  kendall<-corr.test(t(tab),method="kendall",adjust="BH",ci=FALSE)
  kendall<-flattenCorrMatrix(kendall$r)
  kendall<-kendall[order(kendall$row),]
  
  #### Spearman
  spearman<-corr.test(t(tab),method="spearman",adjust="BH",ci=FALSE)
  spearman<-flattenCorrMatrix(spearman$r)
  spearman<-spearman[order(spearman$row),]
  
  #### NMI
  MI <- mutualInfoAdjacency(
  t(tab),
  discretizeColumns = T,
  entropyEstimationMethod = "MM",
  numberBins = NULL)

  NMI <- MI$AdjacencySymmetricUncertainty
  nmi<-flattenCorrMatrix(NMI)
  nmi<-nmi[order(nmi$row),]

  #### Biweight Midcorrelation
  bicor<-bicorAndPvalue(t(tab), y=NULL)
  bicor<-flattenCorrMatrix(bicor$bicor)
  bicor<-bicor[order(bicor$row),]

  scores<-data.frame("gene1"=kendall$row,"gene2"=kendall$column,"kendall"=kendall$cor,"spearman"=spearman$cor,"nmi"=nmi$cor,"bicor"=bicor$cor)

  return(scores)
}
```

### 1.2 BEST TOPOLOGICAL TH (LOG-LOG)
```{r}
LogLogThr2 <- function(net, start, end, bypass){
  Freqs <- data.frame()
  for (x in seq(start, end, bypass)) {
    net <- delete.edges(net, E(net)[ abs(weight) < x ])
    net <- delete.vertices(net, which(igraph::degree(net) < 1))
    
    if (sum(degree(net)) != 0) {
      Freq <- as.data.frame(table(degree(net)))
      colnames(Freq) <- c("degree", "AF")
      Freq$degree <- as.numeric(Freq$degree)
      Freq$RF <- Freq$AF / sum(Freq$AF)
      Freq$Thr <- as.numeric(x)
     
      #Add linear model 
      lmDeg <- lm(log(RF) ~ log(degree), data = Freq)
      Freq$r <- summary(lmDeg)$adj.r.squared
      Freqs <- rbind(Freqs, Freq)
    }
  }
    Freqs<-Freqs[order(Freqs$r,decreasing = T),]
    return(as.double(Freqs[1,4]))
}
```

```{r}
dataframe_best<-function(score){
  best_th<-c()
  for (i in 1:4){
    values<-score[,c(1,2,i+2)]
    colnames(values)[3]<-"weight"
    HP <- graph_from_data_frame(values, directed=FALSE)
    if(i==3){end=1}
    else{end<-boxplot(abs(values$weight),plot=F)$stats[5,]}
    best_th<-c(best_th,LogLogThr2(HP,0,end,0.1))
  }
  
  best_thr<-data.frame(t(best_th))
  colnames(best_thr)<-c("kendall","spearman","nmi","bicor")
  return(best_thr)
}
```

### 1.3 ID CONVERSION
```{r}
id_conversion<-function(my_data){
  string_db <- STRINGdb$new( version="11", species=9606, score_threshold=0, input_directory="")
  n_columns<-(dim(my_data)[2])
  scores_mapped <- string_db$map(my_data, c("gene1"), removeUnmappedRows = TRUE)
  colnames(scores_mapped)[n_columns+1]<-"String1"
  scores_mapped <- string_db$map(scores_mapped, "gene2", removeUnmappedRows = TRUE)
  colnames(scores_mapped)[n_columns+2]<-"String2"

  scores_mapped<-scores_mapped[,c(n_columns+1,n_columns+2,3:n_columns)]
  return(scores_mapped)
}
```

### 1.4 T/F COMBINATIONS + AVG(TRUE)

```{r}
create_all_comb<-function(){
  all_comb<-data.frame(
    (c(T,T,T,T)),(c(T,T,T,F)),(c(T,T,F,T)),
    (c(T,F,T,T)),(c(F,T,T,T)),(c(T,T,F,F)),
    (c(T,F,T,F)),(c(T,F,F,T)),(c(F,T,T,F)),
    (c(F,T,F,T)),(c(F,F,T,T)),(c(T,F,F,F)),
    (c(F,T,F,F)),(c(F,F,T,F)),(c(F,F,F,T))
  )
  all_comb<-data.frame(t(all_comb))
  rownames(all_comb)<-c("K.S.N.B","K.S.N","K.S.B","K.N.B","S.N.B","K.S","K.N","K.B","S.N","S.B","N.B","K","S","N","B")
  colnames(all_comb)<-c("kendall","spearman","NMI","Bicor")
  return(all_comb)
}
```

```{r}
avg_values<-function(network_mapped, all_comb){
  data_abs<-network_mapped[,c(1,2)]
  data_abs[,c(3,4,5,6)]<-abs(network_mapped[,c(3,4,5,6)])
  for (k in 1:15){
    True_index<-which( as.character(all_comb[k,]) %in% T)
    True_index<-True_index+2
    if(length(True_index)>1){network_mapped[,k+7]<-rowMeans(data_abs[,True_index])}
    else{network_mapped[,k+7]<-data_abs[,True_index]}
    }
  
  for (i in 1:15){
    colnames(network_mapped)[i+7]<-rownames(all_comb)[i]
  } 
  return(network_mapped)
}
```

### 1.5 STRING VALIDATION


```{r}
# This function prints the roc curves and calculates the auroc values for each combination 

roc_and_auroc<-function(network_mapped,all_comb){
  col <-rainbow(4)
  col_graph<-c(col[1],rep(col[2],4),rep(col[3],6),rep(col[4],4))
  auroc_data<-c()
  for (i in 1:15){
    roc_<-roc(network_mapped$diagnostic,network_mapped[,i+7])
    if (i==1){plot.roc(roc_, col=col_graph[i])}
    else{lines.roc(roc_,col=col_graph[i])}
    auroc_data<-c(auroc_data,auc(roc_))
  }
  legend("bottomright", legend=row.names(all_comb), col=col_graph, lwd=2)
  return(data.frame("pred"=row.names(all_comb),"number"=c(4,rep(3,4),rep(2,6),rep(1,4)),"auroc"=auroc_data))
}
```

```{r}
first_part_total<-function(normalized_count){
  # Scores calculation
  data_score<-scores(normalized_count)
  
  #Best_Thresholds
  dataframe_best_th<-dataframe_best(data_score)
  
  # IDs conversion
  score_converted<-id_conversion(data_score)
  
  # Importing STRING
  string<-read.table("string_homosapiens.txt",sep=" ",header=T)
  string<-string[string$coexpression>0,c(1,2,6)]
  
  # GS creation and comparison with my data
  GS <- string[string$protein1 %in% score_converted$String1 & string$protein2 %in% score_converted$String2,]
  
  #Diagnostic column
  #score_converted$check <- ifelse(is.na(match(paste0(score_converted$String1, score_converted$String2),paste0(GS$protein1, GS$protein2))), FALSE, TRUE)
  GS <- GS[order(as.character(GS$protein1, GS$protein2)),] %>% unite("rel", protein1:protein2, na.rm = TRUE, remove = FALSE)
  score_converted<-score_converted[order(as.character(score_converted$String1, score_converted$String2)),] %>% unite("rel", String1:String2, na.rm = TRUE, remove = FALSE)

  score_converted$diagnostic<-score_converted$rel %in% GS$rel
  score_converted$rel<-NULL
  
  ### This daframe shows all the possible combinations with at lest one TRUE
  all_comb<-create_all_comb()

  # Average values of the TRUE values for each combination
  score_converted<-avg_values(score_converted,all_comb)
  
  # ROC curves and auroc values
  auroc_<-roc_and_auroc(score_converted,all_comb)
  return(list("score"=data_score,"best_th"=dataframe_best_th,"converted"=score_converted,"auroc"=auroc_,"GS"=GS))
}
```

### 1.6 LES + N_LES COMBINED

```{r}
data_boxplot<-function(auroc1,auroc2){
  merge_df<-rbind(auroc1,auroc2)
  data4<-merge_df[merge_df$number==4,]$auroc
  data3<-merge_df[merge_df$number==3,]$auroc
  data2<-merge_df[merge_df$number==2,]$auroc
  data1<-merge_df[merge_df$number==1,]$auroc
  results<-list("4"=data4,"3"=data3,"2"=data2,"1"=data1)
  boxplot(results,col=rainbow(4),xlab="Number of classifiers",ylab="auROC",ylim=c(0.545,0.565))
  
  best_median<-data.frame("classifier"=c(4,3,2,1),"median"=c(median(data4),median(data3),median(data2),median(data1)))
  best_median<-best_median[order(best_median$median,decreasing=T),]
  return(best_median)
}

```

```{r warning=FALSE}
first_lesional_result<-first_part_total(normalized_count_AL)
first_nonlesional_result<-first_part_total(normalized_count_NL)
first_auroc_combined<-data_boxplot(first_lesional_result$auroc,first_nonlesional_result$auroc)
first_auroc_combined
### The first row of "final" dataframe contains the best number of classifiers
first_best_classifier<-first_auroc_combined[1,1]
GS<-first_lesional_result$GS
```

### 1.7 OVERT TH

```{r}
TrueAndFalse<-function(tab,best_thr){
  trueandfalse<-tab[,c(1,2)]
  trueandfalse$kendall<-ifelse(abs(tab$kendall)>=best_thr[1,1],T,F)
  trueandfalse$spearman<-ifelse(abs(tab$spearman)>=best_thr[1,2],T,F)
  trueandfalse$nmi<-ifelse(abs(tab$nmi)>=best_thr[1,3],T,F)
  trueandfalse$bicor<-ifelse(abs(tab$bicor)>=best_thr[1,4],T,F)
  
  return(trueandfalse)
}
```

```{r}
extract_interaction<-function(score,best_th,best_comb){
  Over<-TrueAndFalse(score,best_th)
  Over$nT<-(Over$nmi + Over$kendall + Over$spearman + Over$bicor)
  final_bool<-Over[Over$nT==best_comb,]
  final_score<-score[is.na(match(paste0(score$gene1,score$gene2),paste0(final_bool$gene1, final_bool$gene2)))==F,]
  final_list<-list("score"=final_score,"bool"=final_bool)
  
  return(final_list)
}
```


```{r}
first_opt_les<-extract_interaction(first_lesional_result$score,first_lesional_result$best_th,first_best_classifier)
first_opt_Nles<-extract_interaction(first_nonlesional_result$score,first_nonlesional_result$best_th,first_best_classifier)
first_opt_les$bool$nT<-NULL
first_opt_Nles$bool$nT<-NULL
```


### 2.1 GRAPH CREATION WITH AVG_TRUE

```{r}
# This function prints a graph using VisNetwork package
vis_graph<-function(g){
  nodes<-data.frame("id"=V(g)$name)
  edges<-data.frame(get.edgelist(g))
  colnames(edges)<-c("from","to")
  visNetwork(nodes,edges,height = "700px", width = "100%")
}
```

```{r}
create_graph<-function(score,bool){
  score$sign<-ifelse(score$kendall*score$spearman*score$nmi*score$bicor>0,1,-1)
  data_abs<-score[,c(1,2)]
  data_abs[,c(3,4,5,6)]<-abs(score[,c(3,4,5,6)])
  
  data_abs$kendall2<-ifelse(bool$kendall==T,data_abs$kendall,NA)
  data_abs$spearman2<-ifelse(bool$spearman==T,data_abs$spearman,NA)
  data_abs$nmi2<-ifelse(bool$nmi==T,data_abs$nmi,NA)
  data_abs$bicor2<-ifelse(bool$bicor==T,data_abs$bicor,NA)
  score$weight<-rowMeans(data_abs[,c(7,8,9,10)], na.rm=T)

  score$weight<-score$weight*score$sign
  
  g<-graph_from_data_frame(score[,c(1,2,8)],directed=F)
  E(g)$abs<-abs(E(g)$weight)
  E(g)$inverted<-1-E(g)$abs
  return(g)
}
```

```{r}
first_les_graph<-create_graph(first_opt_les$score,first_opt_les$bool)
first_Nles_graph<-create_graph(first_opt_Nles$score,first_opt_Nles$bool)
```

### 2.3 NETWORK CONTROL

```{r}
from_network_to_auc<-function(network,GS){
  interactions<-data.frame(get.edgelist(network))
  interactions$weight<-(E(network)$weight)
  colnames(interactions)<-c("gene1","gene2","weight")
  converted<-id_conversion(interactions)
  
  converted<-converted[order(as.character(converted$String1,converted$String2)),] %>% unite("rel", String1:String2, na.rm = TRUE, remove = FALSE)

  converted$diagnostic<-converted$rel %in% GS$rel
  converted$rel<-NULL
  return(roc(converted$diagnostic,abs(converted$weight)))
}
```

```{r}
summary_net<-function(les,Nles,GS){
  summary_data<-data.frame("nodes"=c(length(V(les)),length(V(Nles))),"edges"=c(length(E(les)),length(E(Nles))),"auc"=c(auc(from_network_to_auc(les,GS)),auc(from_network_to_auc(Nles,GS))))
  rownames(summary_data)<-c("Les","Nles")
  return(summary_data)
}
```


```{r warning=FALSE}
first_summary<-summary_net(first_les_graph,first_Nles_graph,GS)
```

### 2.4 GREEDY OPTIMIZATION WITH MST

```{r}
automatic_optimization<-function(g){
  greedy<-mst(g,weights = E(g)$inverted)
  return(greedy)
}
```


```{r}
second_les_graph<-automatic_optimization(first_les_graph)
second_Nles_graph<-automatic_optimization(first_Nles_graph)
```


```{r warning=FALSE}
second_summary<-summary_net(second_les_graph,second_Nles_graph,GS)
```

### 3.1 HUBS IDENTIFICATION

```{r}
identify_hub<-function(g){
  degree<-data.frame("name"=V(g)$name,"degree"=degree(g))
  th<-boxplot(degree$degree,plot=F)$stats[4,]
  hub<-degree[degree$degree>th,1]
  return(hub)
}
```

### 3.2 ADD HUBS INTERACTIONS 

```{r}
add_hub_original_interaction<-function(hubs, first, second,th){
  first_edges<-igraph::as_data_frame(first,what="edges")
  hubs_interaction<-first_edges[first_edges$from %in% hubs | first_edges$to %in% hubs,]
  hubs_interaction_relevant<-hubs_interaction[abs(hubs_interaction$weight)>th,]
  
  graph_new<-second
  for (k in 1:dim(hubs_interaction_relevant)[1]){
    if (are_adjacent(graph_new,hubs_interaction_relevant[k,1],hubs_interaction_relevant[k,2])==FALSE){
      graph_new<-graph_new+edge(hubs_interaction_relevant[k,1],hubs_interaction_relevant[k,2],"weight"=hubs_interaction_relevant[k,3])}
  }
  
  return(graph_new)
}
```


```{r}
id_conversion2<-function(my_data,sd){
  n_columns<-(dim(my_data)[2])
  scores_mapped <- sd$map(my_data, c("gene1"), removeUnmappedRows = TRUE)
  colnames(scores_mapped)[n_columns+1]<-"String1"
  scores_mapped <- sd$map(scores_mapped, "gene2", removeUnmappedRows = TRUE)
  colnames(scores_mapped)[n_columns+2]<-"String2"

  scores_mapped<-scores_mapped[,c(n_columns+1,n_columns+2,3:n_columns)]
  return(scores_mapped)
}
```

```{r}
convert_and_compare<-function(network,GS,sd){
  interactions<-data.frame(get.edgelist(network))
  interactions$weight<-(E(network)$weight)
  colnames(interactions)<-c("gene1","gene2","weight")
  converted<-id_conversion2(interactions,sd)
  
  converted<-converted[order(as.character(converted$String1,converted$String2)),] %>% unite("rel", String1:String2, na.rm = TRUE, remove = FALSE)

  converted$diagnostic<-converted$rel %in% GS$rel
  converted$rel<-NULL
  return(roc(converted$diagnostic,abs(converted$weight)))
}
```

```{r}
best_th_additional<-function(first,second,start,end,bypass,GS){
  string_db <- STRINGdb$new( version="11", species=9606, score_threshold=0, input_directory="")
  
  hub<-identify_hub(second)
  th<-c()
  auc_<-c()
  
  for (i in seq(from=start, to=end, by=bypass)){
    new<-add_hub_original_interaction(hub, first, second, i)
    roc_obj<-convert_and_compare(new,GS,string_db)
    th<-c(th,i)
    auc_<-c(auc_,auc(roc_obj))
  }
  return(data.frame("th"=th,"auc"=auc_))
}
```

```{r warning=FALSE}
third_les_addition<-best_th_additional(first_les_graph,second_les_graph,0.5,max(abs(E(first_les_graph)$weight)),0.01,GS)
third_Nles_addition<-best_th_additional(first_Nles_graph,second_Nles_graph,0.5,max(abs(E(first_Nles_graph)$weight)),0.01,GS)

```

### 3.3 COMPARISON 
```{r}
comp<-function(addition,second){
  windows(width=10, height=8)
  plot(addition[[1]], ylim=c(0.53,0.73),main="Lesional",cex.lab=1.5, cex.axis=1.5, cex.main=1.5,cex=2.5,type="l",lwd=2)
  abline(h=second[1,3],col="red",lwd=2)
  legend("topleft", legend="auc without additional interactions", col="red", lwd=1,cex=1.5)
  windows(width=10, height=8)
  plot(addition[[2]],ylim=c(0.53,0.68),main="Non-Lesional",cex.lab=1.5, cex.axis=1.5, cex.main=1.5,cex=2.5,type="l",lwd=2)
  abline(h=second[2,3],col="red",lwd=2)
  legend("topleft", legend="auc without additional interactions", col="red", lwd=1,cex=1.5)
  
  return(list("Les"=addition[[1]][addition[[1]]$auc==max(addition[[1]]$auc),1],"Nles"=addition[[2]][addition[[2]]$auc==max(addition[[2]]$auc),1]))
}
```

```{r}
third_best_th<-comp(list(third_les_addition,third_Nles_addition),second_summary)
```

```{r}

third_les_graph<-add_hub_original_interaction(identify_hub(second_les_graph),first_les_graph,second_les_graph,third_best_th$Les)
third_Nles_graph<-add_hub_original_interaction(identify_hub(second_Nles_graph),first_Nles_graph,second_Nles_graph,third_best_th$Nles)

third_summary<-summary_net(third_les_graph,third_Nles_graph,GS)

```

```{r}
write.csv(identify_hub(third_les_graph),"hub_les")
```



### 4.1 NETWORKS AFTER ENSEMBLE STRATEGY
```{r}
first_summary
```

### 4.2 NETWORKS AFTER MST

```{r}
second_summary
```

#### 4.3 NETWORKS AFTER ADDING INTERACTIONS TO HUBS
```{r}
third_summary
```


### 5 FINAL COMPARISON


```{r}
eng1_AL<-read.table("EngNET1_AL.txt",header=T)
eng1_NL<-read.table("EngNET1_NL.txt",header=T)
```


```{r}
log_fitting<-function(net){
    Freq <- as.data.frame(table(degree(net)))
    colnames(Freq) <- c("degree", "AF")
    Freq$degree <- as.numeric(Freq$degree)
    Freq$RF <- Freq$AF / sum(Freq$AF)
 
    lmDeg <- lm(log(RF) ~ log(degree), data = Freq)
    return(summary(lmDeg)$adj.r.squared)
}
```


```{r}
networks_info<-function(net,GS){
  r<-log_fitting(net)
  roc_obj<-from_network_to_auc(net,GS)
  edg<-length(E(net))
  vert<-length(V(net))
  
  return(list("roc"=roc_obj,"r"=r,"vert"=vert,"edg"=edg))
}
```


```{r}
final_validation<-function(score,th,eng1,eng2,GS){
  
  kendall<-score[abs(score$kendall)>th$kendall,c(1,2,3)]
  colnames(kendall)[3]<-"weight"
  kendall_net<-graph_from_data_frame(kendall,directed=F)
  info_kendall<-networks_info(kendall_net,GS)
  
  spearman<-score[abs(score$spearman)>th$spearman,c(1,2,4)]
  colnames(spearman)[3]<-"weight"
  spearman_net<-graph_from_data_frame(spearman,directed=F)
  info_spearman<-networks_info(spearman_net,GS)
  
  nmi<-score[abs(score$nmi)>th$nmi,c(1,2,5)]
  colnames(nmi)[3]<-"weight"
  nmi_net<-graph_from_data_frame(nmi,directed=F)
  info_nmi<-networks_info(nmi_net,GS)
  
  bicor<-score[abs(score$bicor)>th$bicor,c(1,2,6)]
  colnames(bicor)[3]<-"weight"
  bicor_net<-graph_from_data_frame(bicor,directed=F)
  info_bicor<-networks_info(bicor_net,GS)
  
  colnames(eng1)[3]<-"weight"
  eng1_net<-graph_from_data_frame(eng1,directed=F)
  info_eng1<-networks_info(eng1_net,GS)
  
  info_eng2<-networks_info(eng2,GS)
  
  return(list("kendall"=info_kendall,"spearman"=info_spearman,"nmi"=info_nmi,"bicor"=info_bicor,"eng1"=info_eng1,"eng2"=info_eng2))
}


```


```{r}
result_Lesional<-final_validation(first_lesional_result$score,first_lesional_result$best_th,eng1_AL,third_les_graph,GS)
result_non_Lesional<-final_validation(first_nonlesional_result$score,first_nonlesional_result$best_th,eng1_NL,third_Nles_graph,GS)

```

```{r}
print_curves<-function(result){
  windows(width=10,height=8)
  par(pty="s")
  color<-brewer.pal(6,name="Dark2")
  plot.roc(result$kendall$roc,col=color[1],cex.lab=2,cex.axis=1.5)
  lines.roc(result$spearman$roc,col=color[2])
  lines.roc(result$nmi$roc,col=color[3])
  lines.roc(result$bicor$roc,col=color[4])
  lines.roc(result$eng1$roc,col=color[5])
  lines.roc(result$eng2$roc,col=color[6])
  legend("bottomright", legend=c("kendall","spearman","nmi","bicor","EnGNet1","EnGNet2"), col=color, lwd=2,cex=1.5)
}
```

```{r}
summarize_results<-function(result){
  first<-c(auc(result$kendall$roc),auc(result$spearman$roc),auc(result$nmi$roc),auc(result$bicor$roc),auc(result$eng1$roc),auc(result$eng2$roc))
  second<-c(result$kendall$r,result$spearman$r,result$nmi$r,result$bicor$r,result$eng1$r,result$eng2$r)
  third<-c(result$kendall$vert,result$spearman$vert,result$nmi$vert,result$bicor$vert,result$eng1$vert,result$eng2$vert)
  fourth<-c(result$kendall$edg,result$spearman$edg,result$nmi$edg,result$bicor$edg,result$eng1$edg,result$eng2$edg)
 table_final<-data.frame("auc"=first,"fitting_power_law"=second,"nodes"=third,"edges"=fourth)
 rownames(table_final)<-c("kendall","spearman","nmi","bicor","EnGNet1","EnGNet2")
 return(table_final)
}
```


```{r}
print_curves(result_Lesional)
print_curves(result_non_Lesional)
summarize_results(result_Lesional)
summarize_results(result_non_Lesional)

```


```{r}
write.csv(igraph::as_data_frame(third_les_graph,what="edges")[,c(1:3)],"final_les")
write.csv(igraph::as_data_frame(third_Nles_graph,what="edges")[,c(1:3)],"final_Nles")
```


```{r}
library("esquisse")
cluster<-read.csv("final_les_default_node.csv")
dimensiona_cluster<-as.data.frame(table(cluster$X__glayCluster))
c6<-cluster[cluster$X__glayCluster==6,]$name
write.csv(V(third_les_graph)$name,"lesional_entire")

cluego<-read.table("clueGO_MF_les.txt",sep="\t",header=T)
cluego<-cluego[order(cluego$Term.PValue.Corrected.with.Bonferroni.step.down),]
cluego_top10<-cluego[c(1:10),c(3,9)]
cluego_top10$Term.PValue.Corrected.with.Bonferroni.step.down<-log(cluego_top10$Term.PValue.Corrected.with.Bonferroni.step.dow)
cluego_top10<-cluego_top10[order(cluego_top10$Term.PValue.Corrected.with.Bonferroni.step.down),]

esquisser()


library(ggplot2)

ggplot(cluego_top10) +
 aes(x = GOTerm, weight = Term.PValue.Corrected.with.Bonferroni.step.down) +
 geom_bar(fill = "blue") +
 scale_y_continuous(trans = "asn") +
 labs(y = "Terms Log P-value", title = "Molecular Functions") +
 coord_flip() +
 theme_minimal() +
 theme(plot.title = element_text(hjust = 0.5)) +
 ylim(0L, -18L)

```

```{r}
write.csv(first_lesional_result$score,"lesional_scores")
write.csv(first_nonlesional_result$score,"non_lesional_scores")
write.csv(first_lesional_result$best_th,"th_lesional")
write.csv(first_nonlesional_result$best_th,"th_non_lesional")
GS<-first_lesional_result$GS
write.csv(GS,"GS")

```


